

```{r initialize, echo=FALSE,results='hide',message=FALSE,warning=FALSE}
# Initialize!

# Stop R from interpreting strings as factors. 
# When you want factors, you'll know it.
options(stringsAsFactors = FALSE)

# Load up the requisite packages
library(knitr)     # It's a knitr document, after all...
library(to1check)  # All TO1-related functions
library(plyr)      # For the count() and arrange() functions
library(mpmisc)    # For printing data.frames nicely
library(lubridate) # For calculating number of weeks remaining
library(tbdiag)    # For checking QFT and TSPOT results

# Set default chunk options
opts_chunk$set(echo = FALSE,
               results = 'asis',
               message = FALSE,
               warning = FALSE,
               error = TRUE)


# Load the ggplot2 theme
source(file.path("..", "css", "theme_tbesc.r"))
source(file.path("..", "css", "angled_x.r"))


# Load the local info (edit this if your results are wrong)
local_facts <- read.csv("local_facts.csv")

# Load the latest cleaned data
load(local_facts$datapath)

# Set aside those who were successfully enrolled during the 
# in question - we'll generally disregard those who declined 
# or who didn't complete enrollment 

enrolled <- with(to1clean$master,
    StudyID[!CloseReason %in% c("Didn't complete enrollment", 
                                "Withdrew", 
                                "Not eligible") &
            EnrollDate >= as.Date(local_facts$period_start) &
            EnrollDate <= as.Date(local_facts$period_end)]
)

# For checks that should include participants form all times
enrolled_ever <- with(to1clean$master,
    StudyID[!CloseReason %in% c("Didn't complete enrollment", 
                                "Withdrew", 
                                "Not eligible")]
)


# Set up subsets of just the participants enrolled this period
enrolled_master <- to1clean$master[to1clean$master$StudyID %in% enrolled, ]



```

<h1 class='maintitle'>TBESC TO 1 Status Report: `r local_facts$site`</h1>
<h3 class='maintitle'>Enrollment Period: `r paste(local_facts$period_start, "through", local_facts$period_end)`</h3>
<span class='maintitle'>Report generated at `r format(Sys.time())`</span>

## Enrollment Progress
---------------------
```{r}

# Total enrolled so far (I need a better measure of this)
total_enrolled <- length(enrolled)

# Total remaining to meet local target
total_remain <- local_facts$enroll_target - total_enrolled

# Weeks remaining in the enrollment period
weeks_left <- new_interval(Sys.Date(), local_facts$period_end) / 
              duration(num = 1, units = "weeks")

# Average weekly enrollment to make target
weekly_target <- round(total_remain / weeks_left, 1)


```

Total Enrolled to Date: `r total_enrolled`

Enrollment Remaining: `r total_remain`

Weeks Remaining (approximately): `r round(weeks_left, 1)`

Average Weekly Enrollment Required: `r weekly_target`



```{r,results="hide",fig.width = 12, fig.height = 6}
# Plot enrollment progress to date
enrolled_dates <- enrolled_master$EnrollDate

enroll_progress_plot(enrolled_dates,
                     target = local_facts$enroll_target,
                     enroll_start = as.Date(local_facts$period_start),
                     enroll_end = as.Date(local_facts$period_end)) + 
    theme_tbesc +
    angled_x

```

```{r weekly_enroll}

# Show enrollment from the last x weeks

# Convert enrollment dates to weeks
enrolled_weeks <- data.frame(enroll_date = enrolled_dates,
                             enroll_week = format(enrolled_dates, "%Y-%W"))

# Aggregate
weekly_enrolled <- ddply(enrolled_weeks, .var = "enroll_week", .fun = summarise,
    `Week` = min(enroll_date, na.rm = TRUE),
    `Number Enrolled` = length(enroll_date)
)

cat("Enrollment Totals for Last Eight Weeks \n")
dfprintif(tail(weekly_enrolled[ , c("Week", "Number Enrolled")], 8))



# Estimated end of enrollment
# Calculate average enrollment over the last eight weeks
ave_enroll <- mean(tail(weekly_enrolled$"Number Enrolled", 8))

# Crude estimate of the end of enrollment
estimated_end <- format(Sys.Date() + total_remain / ave_enroll *7, 
                        format = "%B %d, %Y"
)

cat("Estimated Completion of Enrollment: ", estimated_end)



```





## Participants with Action Needed
-----------------------------------

### Participants Eligible for Follow-Up
```{r}
fu_report <- calc_fu(to1clean)

names(fu_report) <- c("StudyID", "Enroll Date", 
                      "FU Starts", "FU Ends", "Eligible for FU",
                      "FU Cycle", "Days Left", "Completed")


dfprintif(fu_report,
          norowmsg = "No participants require follow-up at this time.")

```



### Triple-Negative Participants to Close
```{r to_close}
# Identify triple neg participants to close (and sort by visit date)
tripnegtoclose <- arrange(to_close(to1clean), EnrollDate)

# Flag contacts - they won't necessarily be closed right away, 
# pending 8-week results
tripnegtoclose$contact <- tripnegtoclose$StudyID %in% 
    to1clean$preenrollment$StudyID[to1clean$preenrollment$CloseContact %in% 1]

# Pretty names
names(tripnegtoclose) <- c("StudyID", "Status", "Visit Date", 
                           "TST Neg?", "QFT Neg?",
                           "TSPOT Neg?", "Triple Neg?",
                           "Contact?")

dfprintif(tripnegtoclose,
          norowmsg = "No open triple-negative participants at this time.")

```



### Participants Closed Incorrectly
```{r closed_wrongly}
# Identify triple neg participants to close (and sort by visit date)
closedwrongly <- arrange(closed_check(to1clean), problem, EnrollDate)

# Pretty names
names(closedwrongly) <- c("StudyID", "Visit Date", "Reason Closed", "Problem")

dfprintif(arrange(closedwrongly, `Visit Date`),
         norowmsg = "There are no incorrectly-closed participants at this time.")


```




## Data Quality Checks
------------------------


### QFT Results to Double-Check
```{r qftcheck}

# Calculate QFT results using tbdiag
qfts <- subset(to1clean$qft,
               select = c("StudyID", "dt_placed", 
                          "nil", "tb", "mito", "result",
                          "nil.num", "tb.num", "mito.num",
                          "rerun_nil", "rerun_tb", "rerun_mito", "rerun_result",
                          "rerun_nil.num", "rerun_tb.num", "rerun_mito.num")
)
               
qfts$result_check <- with(qfts, 
                          qft.interp(nil = nil.num, 
                                     tb = tb.num, 
                                     mito = mito.num,
                                     verbosity = "terse")
)


# Identify any discordant results
qfts_discord <- subset(qfts,
                       subset = result != result_check,
                       select = c("StudyID", "dt_placed", 
                                  "nil", "tb", "mito", 
                                  "result", "result_check")
)


# Pretty names
names(qfts_discord) <- c("StudyID", "Date Placed", 
                         "Nil", "TB Antigen", "Mitogen",
                         "DMS Result", "Calculated Result")


# Print
dfprintif(qfts_discord,
          norowmsg = "All recorded QFT results appear to be correct.")


```

### TSPOT Results to Double-Check
```{r tspotcheck}

# Calculate tspot results using tbdiag - exclude any "Test Not Performed" TSPOTs.
tspots <- subset(to1clean$tspot,
                 subset = !result %in% "Test Not Performed",
                 select = c("StudyID", "dt_placed", 
                            "nil", "panel_a", "panel_b", "mito", "result",
                            "nil.num", "panel_a.num", "panel_b.num", "mito.num")
)
               
tspots$result_check <- with(tspots, 
                          tspot.interp(nil = nil.num, 
                                       panel.a = panel_a.num, 
                                       panel.b = panel_b.num,
                                       mito = mito.num,
                                       verbosity = "terse")
)


# Identify any discordant results
tspots_discord <- subset(tspots,
                       subset = result != result_check,
                       select = c("StudyID", "dt_placed", 
                                  "nil", "panel_a", "panel_b", "mito", 
                                  "result", "result_check")
)


# Pretty names
names(tspots_discord) <- c("StudyID", "Date Placed", 
                         "Nil", "Panel A", "Panel B", "Mitogen",
                         "DMS Result", "Calculated Result")


# Print
dfprintif(tspots_discord,
          norowmsg = "All recorded TSPOT results appear to be correct.")

```



### Participants with Follow-ups Outside of the 45 Day Window
```{r}

oobfu <- check_fu(to1clean)

# Pretty names
names(oobfu) <- c("StudyID", "Enrollment Date", "FU Cycle", "FU Date",
                  "Eligibility Started", "Eligibility Ended")

dfprintif(arrange(oobfu, `FU Date`),
          norowmsg = "All follow-ups were completed on eligible dates.")


```



### Participants with TSTs Read Outside of the 44-76 Hour Window
```{r}
winprob <- tst_win_check(to1clean)

winprob_enrolled <- winprob[winprob$StudyID %in% enrolled, ]

# Pretty names
names(winprob_enrolled) <- c("StudyID",
                             "Date/Time Placed", "Placed By",
                             "Date/Time Read", "Read By",
                             "Hours Between")


dfprintif(winprob_enrolled,
          norowmsg = "All TSTs read within the protocol window.")

```



### Participants with Missing TST, QFT, or TSPOT Results
```{r}
# Identify participants with a missing test
testres <- compile_results(to1clean)

# Exclude those who didn't complete enrollment activities
missingtest <- subset(arrange(testres, EnrollDate),
                      subset = (is.na(tst) | 
                                is.na(qft) | 
                                tspot %in% c(NA, "Test Not Performed")) & 
                                StudyID %in% enrolled_ever,
                      select = c("StudyID", "EnrollDate", "tst", "qft", "tspot"))

# Pretty names
names(missingtest) <- c("StudyID", "Visit Date", 
                        "TST Result", "QFT Result", "TSPOT Result")


dfprintif(missingtest,
          norowmsg = "All participants have complete test results at this time.")

```



### Participants with Pre-enrollment vs. Calculated Age Discrepancies
Age is calculated from participant's reported date of birth and their visit date.
```{r}
ageprob <- age_check(to1clean)

ageprob_enrolled <- ageprob[ageprob$StudyID %in% enrolled, ]

# Pretty names
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "preenroll_age"] <- "Pre-enroll Age"
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "calc_age"] <- "Calculated Age"
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "age_diff"] <- "Difference"


dfprintif(ageprob_enrolled,
          norowmsg = paste("\n","All pre-enrollment and calculated ages match."))

```



### Height and Weight
```{r,fig.width=8}
htwts <- htwt_check(to1clean)

# Show the plot (and cancel out theme_tbesc's angled axis text)
htwts$plot + theme_tbesc
```



#### Participants with most-outlying heights/weights in this enrollment period:
```{r}
# Subset to this enrollment period
htwtoutliers_enrolled <- htwts$outlierdf[htwts$outlierdf$StudyID %in% enrolled, ]

# Slightly nicer names
names(htwtoutliers_enrolled) <- c("StudyID", "Height (inches)", "Weight (pounds)")

dfprintif(htwtoutliers_enrolled,
          norowmsg = "No outliers are present in this period's enrollment.")
```



#### Participants missing height and/or weight in this enrollment period:
```{r}
# Subset to this enrollment period
htwtmissing_enrolled <- htwts$missingdf[htwts$missingdf$StudyID %in% enrolled, ]

# Slightly nicer names
names(htwtmissing_enrolled) <- c("StudyID", "Height (inches)", "Weight (pounds)")

dfprintif(htwtmissing_enrolled,
          norowmsg = "All participants have height and weight recorded.")

```



### TSTs with Rare PPD Lot Numbers
```{r}
lotfreq <- count(to1clean$skintest, "PpdLotNumber")

n.rare <- 5

rare_tst_lot <- subset(to1clean$skintest,
                       subset = PpdLotNumber %in% 
                                lotfreq$PpdLotNumber[lotfreq$freq < n.rare],
                       select = c("StudyID", "dt_placed", "TstPlacedBy", "PpdLotNumber"))

# Pretty names
names(rare_tst_lot) <- c("StudyID", "Date Placed", "Placed By", "PPD Lot #")


dfprintif(arrange(rare_tst_lot, `PPD Lot #`),
          norowmsg = paste("All participants' TST lots have", 
                           n.rare, 
                           "or more placements recorded.")
)

```




### QFTs with Rare Lot Numbers
```{r}

# Melt the lots into a single database
lot.melt <- melt(to1clean$qft,
                 id.var = "StudyID",
                 measure.var = c("QftLotNumNil", "QftLotNumTba",
                                 "QftLotNumMit", "QftAssayLotNum")
)

# Pretty names
levels(lot.melt$variable) <- c("Nil", "TB", "Mitogen", "Assay")

# Subset to the rare lots
qftlotfreq <- subset(count(lot.melt, c("variable", "value")),
                     freq < n.rare)

qftlotfreq$flag <- TRUE

lot.probs <- merge(x = lot.melt,
                   y = qftlotfreq[ , c("variable", "value")],
                   by = c("variable", "value")
)



# Pretty names
names(lot.probs) <- c("Tube", "Lot Number", "Study ID")


dfprintif(lot.probs[ , c("Study ID", "Tube", "Lot Number")],
          norowmsg = paste("All participants' QFT lots have", 
                           n.rare, 
                           "or more uses recorded.")
)


```


### Contacts Without Source's State Case Number or GenType

```{r contacts_missing_info}


# Identify participants who are contacts but still pending either a state case number
# or a GenType number

contacts_miss <- subset(to1clean$master,
                        subset = StateCaseNumberIdk %in% 98 |
                                 GenTypeIdk %in% 98,
                        select = c("StudyID", "EnrollDate", "StateCaseNumber", "GenType")
)




dfprintif(arrange(contacts_miss, EnrollDate, StudyID),
          norowmsg = "All contacts appear to have complete source case information.")


```





### Participants with Misspelled Languages

```{r langprob}

# Set up a vector of acceptable language names
langs <- c("Arabic", "Burmese", "Vietnamese", 
           "French", "Haitian", "Chinese",
           "Nepali", "Somali", "Spanish", 
           "Tagalog", "Akan", "Amharic",
           "Portuguese", "Chin", "Chuukese",
           "Dari", "Farsi", "Fulani", "Greek",
           "Hindi", "Hmong", "Ilocano",
           "Indonesian", "Jarai", "Karen",
           "Khmer", "Kirundi", "Korean",
           "Serbian", "Kurdish", "Lao",
           "Malayalam", "Marshallese", 
           "Oromo", "Oromic",
           "Polish", "Punjabi", "Romanian",
           "Russian", "Swahili", "Tamil",
           "Thai", "Tigrinya", "Urdu",
           "")

# Check the enrolled names for validity
langprob <- subset(to1clean$master,
                   subset = !tolower(InterpreterLanguage) %in% tolower(langs),
                   select = c("StudyID", "InterpreterLanguage")
)


# Pretty names
names(langprob) <- c("Study ID", "Language")


dfprintif(langprob,
          norowmsg = "All languages appear to be spelled correctly.")


```


### Participants with Unclassified Treatment Plans (Matt will fix)

```{r weird_plan}

weird_plan <- subset(to1clean$ltbi, 
                     subset = plan %in% "Unknown",
                     select = c("StudyID", "plan",
                                "Isoniazid", "IsoniazidFreq",
                                "Rifampin", "RifampinFreq",
                                "Rifapentine", "RifapentineFreq",
                                "Other", "OtherFreq")
)


dfprintif(weird_plan,
          norowmsg = "All plans are successfully classified.")


```


