

<style type="text/css">

body {
  text-align: center;
  padding-bottom: 20%;
}

table {
  margin-left: auto;
  margin-right: auto;
  border: 1px solid #808080;
  border-collapse: collapse;
}

th {
  background-color: #1F78B4;
  color: #FFFFFF;
  border: 1px solid #808080;
  padding-right: 20px;
  padding-left: 20px;
}

td {
  border: 1px solid #808080;
  padding-right: 20px;
  padding-left: 20px;
}

.maintitle {
  text-align: center;
  padding-top: 0px;
}

h2 {
  text-align: center;
  padding-top: 80px;
}

h3, h4 {
  padding-top: 30px;
}

hr {
  border: 0;
  height: 1px;
  background: #333;
  background-image: -webkit-linear-gradient(left, #ccc, #333, #ccc); 
  background-image:    -moz-linear-gradient(left, #ccc, #333, #ccc); 
  background-image:     -ms-linear-gradient(left, #ccc, #333, #ccc); 
  background-image:      -o-linear-gradient(left, #ccc, #333, #ccc); 
}

</style>



```{r initialize, echo=FALSE,results='hide',message=FALSE,warning=FALSE}
# Initialize!

# Stop R from interpreting strings as factors. 
# When you want factors, you'll know it.
options(stringsAsFactors = FALSE)

# Load up the requisite packages
library(knitr)     # It's a knitr document, after all...
library(to1check)  # All TO1-related functions
library(plyr)      # For the count() and arrange() functions
library(xtable)    # For printing data.frames nicely
library(lubridate) # For calculating number of weeks remaining

# Set default chunk options
opts_chunk$set(echo = FALSE,
               results = 'asis',
               message = FALSE,
               warning = FALSE,
               error = TRUE)


# Load the local info (edit this if your results are wrong)
local_facts <- read.csv("local_facts.csv")

# Load the latest cleaned data
load(local_facts$datapath)

# Set aside those who were successfully enrolled during the 
# in question - we'll generally disregard those who declined 
# or who didn't complete enrollment 

enrolled <- with(to1clean$master,
    StudyId[!CloseReason %in% c("Didn't complete enrollment", "Withdrew", "Not eligible") &
            VisitDate >= as.Date(local_facts$period_start) &
            VisitDate <= as.Date(local_facts$period_end)]
)


# Set up subsets of just the participants enrolled this period
enrolled_master <- to1clean$master[to1clean$master$StudyId %in% enrolled, ]



# Set up default print arguments for printing tables:
# xtable() makes data.frames more suitable for display
# format() converts all of the data.frame comments to character*;
# print() writes the xtable object to HTML

# *print() for xtable throws a tantrum over Date and POSIXct variables,
# so they have to be converted to character before printing 

dfprint <- function(df, printdigits = 2) {
    print(
        xtable(format(df, 
                      na.encode = FALSE, 
                      digits = printdigits, 
                      nsmall = printdigits), 
               align = c("l", "l", rep("c", ncol(df) - 1))
        ),
        type = "html",
        include.rownames = FALSE,
        NA.string = "-")
}




```

<h1 class='maintitle'>TBESC TO 1 Status Report: `r local_facts$site`</h1>
<h3 class='maintitle'>Enrollment Period: `r paste(local_facts$period_start, "through", local_facts$period_end)`</h3>
<span class='maintitle'>Report generated at `r format(Sys.time())`</span>

## Enrollment Progress
---------------------
```{r}

# Total enrolled so far (I need a better measure of this)
total_enrolled <- length(enrolled)

# Total remaining to meet local target
total_remain <- local_facts$enroll_target - total_enrolled

# Weeks remaining in the enrollment period
weeks_left <- new_interval(Sys.Date(), local_facts$period_end) / 
              duration(num = 1, units = "weeks")

# Average weekly enrollment to make target
weekly_target <- round(total_remain / weeks_left, 1)
```

Total Enrolled to Date: `r total_enrolled`

Enrollment Remaining: `r total_remain`

Weeks Remaining (approximately): `r round(weeks_left, 1)`

Average Weekly Enrollment Required: `r weekly_target`



```{r,results="hide",fig.width = 12, fig.height = 6}
# Plot enrollment progress to date
enrolled_dates <- enrolled_master$VisitDate

enroll_progress_plot(enrolled_dates,
                     target = local_facts$enroll_target,
                     enroll_start = as.Date(local_facts$period_start),
                     enroll_end = as.Date(local_facts$period_end)
)

```

```{r weekly_enroll}

# Show enrollment from the last x weeks

# Convert enrollment dates to weeks
enrolled_weeks <- data.frame(enroll_date = enrolled_dates,
                             enroll_week = format(enrolled_dates, "%Y-%W"))

# Aggregate
weekly_enrolled <- ddply(enrolled_weeks, .var = "enroll_week", .fun = summarise,
    `Week` = min(enroll_date, na.rm = TRUE),
    `Number Enrolled` = length(enroll_date)
)

cat("Enrollment Totals for Last Eight Weeks \n")
dfprint(tail(weekly_enrolled[ , c("Week", "Number Enrolled")], 8))




```





## Participants with Action Needed
-----------------------------------

### Participants Eligible for Follow-Up
```{r}
fu_report <- calc_fu(to1clean)

names(fu_report) <- c("StudyID", "Enroll Date", 
                      "FU Starts", "FU Ends", "Eligible for FU",
                      "FU Cycle", "Days Left", "Completed")


if(nrow(fu_report) > 0) { dfprint(fu_report) } else {
  cat("No participants require follow-up at this time.")
} 
```



### Triple-Negative Participants to Close
```{r to_close}
# Identify triple neg participants to close (and sort by visit date)
tripnegtoclose <- arrange(to_close(to1clean), VisitDate)

# Pretty names
names(tripnegtoclose) <- c("StudyId", "Status", "Visit Date", 
                           "TST Neg?", "QFT Neg?",
                           "TSPOT Neg?", "Triple Neg?")

if(nrow(tripnegtoclose) > 0) { dfprint(tripnegtoclose) } else {
  cat("No open triple-negative participants at this time.")
} 
```



### Participants Closed Incorrectly
```{r closed_wrongly}
# Identify triple neg participants to close (and sort by visit date)
closedwrongly <- arrange(closed_check(to1clean), close_problem, VisitDate)

# Pretty names
names(closedwrongly) <- c("StudyId", "Visit Date", "Reason Closed", "Problem")

if(nrow(closedwrongly) > 0) { dfprint(arrange(closedwrongly, `Visit Date`)) } else {
  cat("There are no incorrectly-closed participants at this time.")
} 

```




## Data Quality Checks
------------------------

### Participants with TSTs Read Outside of the 44-76 Hour Window
```{r}
winprob <- tst_win_check(to1clean)

winprob_enrolled <- winprob[winprob$StudyId %in% enrolled, ]

# Pretty names
names(winprob_enrolled) <- c("StudyId",
                             "Date/Time Placed", "Placed By",
                             "Date/Time Read", "Read By",
                             "Hours Between")


if(nrow(winprob_enrolled) > 0) { dfprint(winprob_enrolled) } else {
  cat("All TSTs read within the protocol window.")
} 
```



### Participants with Missing TST, QFT, or TSPOT Results
```{r}
# Identify participants with a missing test
testres <- compile_results(to1clean)

testres_enrolled <- testres[testres$StudyId %in% enrolled, ]

missingtest <- subset(arrange(testres_enrolled, VisitDate),
                      subset = (is.na(tst) | is.na(qft) | is.na(tspot)) & 
                               StudyId %in% enrolled,
                      select = c("StudyId", "VisitDate", "tst", "qft", "tspot"))

# Pretty names
names(missingtest) <- c("StudyId", "Visit Date", 
                        "TST Result", "QFT Result", "TSPOT Result")


if(nrow(missingtest) > 0) { dfprint(missingtest) } else {
  cat("All participants have complete test results at this time.")
} 
```



### Participants with Pre-enrollment vs. Calculated Age Discrepancies
Age is calculated from participant's reported date of birth and their visit date.
```{r}
ageprob <- age_check(to1clean)

ageprob_enrolled <- ageprob[ageprob$StudyId %in% enrolled, ]

# Pretty names
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "preenroll_age"] <- "Pre-enroll Age"
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "calc_age"] <- "Calculated Age"
names(ageprob_enrolled)[names(ageprob_enrolled) %in% "age_diff"] <- "Difference"


if(nrow(ageprob_enrolled) > 0) { dfprint(ageprob_enrolled) } else {
  cat("\n","All pre-enrollment and calculated ages match.")
} 
```



### Height and Weight
```{r,fig.width=8}
htwts <- htwt_check(to1clean)

# Show the plot
htwts$plot
```



#### Participants with most-outlying heights/weights:
```{r}
# Subset to this enrollment period
htwtoutliers_enrolled <- htwts$outlierdf[htwts$outlierdf$StudyId %in% enrolled, ]

# Slightly nicer names
names(htwtoutliers_enrolled) <- c("StudyId", "Height (inches)", "Weight (pounds)")

dfprint(htwtoutliers_enrolled)
```



#### Enrolled participants missing height and/or weight:
```{r}
# Subset to this enrollment period
htwtmissing_enrolled <- htwts$missingdf[htwts$missingdf$StudyId %in% enrolled, ]

# Slightly nicer names
names(htwtmissing_enrolled) <- c("StudyId", "Height (inches)", "Weight (pounds)")

if(nrow(htwtmissing_enrolled) > 0) { dfprint(htwtmissing_enrolled) } else {
  cat("All participants have height and weight recorded.")
} 
```



### TSTs with Rare PPD Lot Numbers
```{r}
lotfreq <- count(to1clean$skintest, "PpdLotNumber")

n.rare <- 5

rare_tst_lot <- subset(to1clean$skintest,
                       subset = PpdLotNumber %in% 
                                lotfreq$PpdLotNumber[lotfreq$freq < n.rare],
                       select = c("StudyId", "dt_placed", "TstPlacedBy", "PpdLotNumber"))

# Pretty names
names(rare_tst_lot) <- c("StudyId", "Date Placed", "Placed By", "PPD Lot #")


if(nrow(rare_tst_lot) > 0) { 
    dfprint(arrange(rare_tst_lot, `PPD Lot #`)) } else {
  cat("All participants TST lots have", n.rare, "or more placements recorded.")
} 
```




